Titeln på avhandlingens språk

### 2022-12-13 appendices.tex
fixes for IEEE ToMC

\appendix{}\label[appendixwithoutnumber]{appx1}
% \subsection*{Sampling optimisation}

@@

By making use of this general solution, we can also prove the results given in \cref{ssec:optimization:samples}, where we modify the problem and find the optimum sampling instants that minimize the expected number of samples for a given upper bound $w_0$ for the expected wait time.
First note that the general solution has constants $\alpha$ and $\beta$ that correspond to the weights given to the cost of sampling and cost of waiting, respectively.
The optimization criteria changes from minimizing wait time to minimizing the number of samples when the ratio $\frac{\alpha}{\beta}$ goes from zero to infinity.
Since any positive real value is valid for this ratio, one can achieve any valid point $(\mathbb{E}[\mathcal{S}],\mathbb{E}[\mathcal{W}])$ via simply by varying the ratio $\frac{\alpha}{\beta}$.
\newpage%
Furthermore, since the sampling instants are aperiodic and can take any positive real values, the bound will be tight at the optimum. 
% This is because (1) a higher bound on $\mathbb{\mathcal{W}}$ is always associated with a lower optimum on $\mathbb{\mathcal{S}}$ and (2) any $\mathbb{\mathcal{W}}$ can be achieved, for instance by a scaling all the sampling instance of a given policy by an appropriate constant.
Hence, to solve for the modified optimization problem explained in \cref{ssec:optimization:samples} that minimizes $\mathbb{E}[\mathcal{S}]$ with an upper bound $w_0$ on $\mathbb{E}[\mathcal{W}]$, we equate \cref{Ew} to $w_0$, find the corresponding $\frac{\alpha}{\beta}$, and find the optimum set of sampling instants by plugging this ratio into \cref{tnRayleigh}.
\begin{alignat*}{1}
\mathbb{E}[\mathcal{W}]&=\int_{0}^{\infty}\dfrac{1}{2r(t)}f_\mathcal{T}(t)\,\mathrm{d}t.\nonumber\\
&=\int_{0}^{\infty}\frac{1}{2}\sqrt{\frac{2\alpha\sigma^2}{\beta t}}\cdot \frac{t}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\int_{0}^{\infty}\frac{\sqrt{t}}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\int_{0}^{\infty}y^{-1/4}e^{-y}\mathrm{d}y\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\mathlarger{\Gamma}(\tfrac{3}{4}),\\
% &\approx 0.728637\sqrt{\frac{\alpha\sigma}{\beta}}\\
\intertext{%
    where $\mathlarger{\Gamma(x)}$ is the gamma function.
    Thus, when the upper bound $w_0$ is tight,
}
\mathbb{E}[\mathcal{W}]&=w_0=\sqrt{\frac{\alpha\sigma}{2\sqrt{2}\beta}}\mathlarger{\Gamma}(\tfrac{3}{4})\\
\Rightarrow\frac{\alpha}{\beta}&=\frac{w_0^2}{\sigma}\frac{2\sqrt{2}}{(\mathlarger{\Gamma}(\tfrac{3}{4}))^2}\\
% &=1.88355\frac{w_0^2}{\sigma}
&\approx1.9\frac{w_0^2}{\sigma}.
\end{alignat*}

>>>>

\clearpage%
\pagestyle{empty}%
\appendix{}\label[appendixwithoutnumber]{appx1}
% \subsection*{Sampling optimisation}

@@

By making use of this general solution, we can also prove the results given in \cref{ssec:optimization:samples}, where we modify the problem and find the optimum sampling instants that minimize the expected number of samples for a given upper bound $w_0$ for the expected wait time.
First note that the general solution has constants $\alpha$ and $\beta$ corresponding to the weights given to the cost of sampling and waiting, respectively.
The optimization criteria changes from minimizing wait time to minimizing the number of samples when the ratio $\frac{\alpha}{\beta}$ goes from zero to infinity.
Since any positive real value is valid for this ratio, one can achieve any valid point $(\mathbb{E}[\mathcal{S}],\mathbb{E}[\mathcal{W}])$ via simply by varying the ratio $\frac{\alpha}{\beta}$.
\newpage%
Furthermore, since the sampling instants are aperiodic and can take any positive real values, the bound will be tight at the optimum. 
% This is because (1) a higher bound on $\mathbb{\mathcal{W}}$ is always associated with a lower optimum on $\mathbb{\mathcal{S}}$ and (2) any $\mathbb{\mathcal{W}}$ can be achieved, for instance by a scaling all the sampling instance of a given policy by an appropriate constant.
Hence, to solve for the modified optimization problem explained in \cref{ssec:optimization:samples} that minimizes $\mathbb{E}[\mathcal{S}]$ with an upper bound $w_0$ on $\mathbb{E}[\mathcal{W}]$, we equate \cref{Ew} to $w_0$, find the corresponding $\frac{\alpha}{\beta}$, and find the optimum set of sampling instants by plugging this ratio into \cref{tnRayleigh}.
\begin{alignat*}{1}
\mathbb{E}[\mathcal{W}]&=\int_{0}^{\infty}\dfrac{1}{2r(t)}f_\mathcal{T}(t)\,\mathrm{d}t.\nonumber\\
&=\int_{0}^{\infty}\frac{1}{2}\sqrt{\frac{2\alpha\sigma^2}{\beta t}}\cdot \frac{t}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\int_{0}^{\infty}\frac{\sqrt{t}}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\int_{0}^{\infty}y^{-1/4}e^{-y}\mathrm{d}y\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\mathlarger{\Gamma}(\tfrac{3}{4}),\\
% &\approx 0.728637\sqrt{\frac{\alpha\sigma}{\beta}}\\
\intertext{%
    where $\mathlarger{\Gamma(x)}$ is the gamma function.
    Thus, when the upper bound $w_0$ is tight,
}
\mathbb{E}[\mathcal{W}]&=w_0=\sqrt{\frac{\alpha\sigma}{2\sqrt{2}\beta}}\mathlarger{\Gamma}(\tfrac{3}{4})\\
\Rightarrow\frac{\alpha}{\beta}&=\frac{w_0^2}{\sigma}\frac{2\sqrt{2}}{(\mathlarger{\Gamma}(\tfrac{3}{4}))^2}\\
% &=1.88355\frac{w_0^2}{\sigma}
&\approx1.9\frac{w_0^2}{\sigma}.
\end{alignat*}
